Blame and Coercion: Together Again for the Second Time

### 2019-10-16 paper.tex
fix typing of cast cal
minor fixes

@@

	Term typing
	\fbox{$ \judgetype{\Gamma}{e}{T} $}
	\begin{gather*}
		\inference{
			S \sim T & \Gamma \vdash e : S 
		}{
			\judgetype{\Gamma}{\eOOcast{e}{T_1}{l}{T_2}}{T_2}
		} \quad
		\inference{
		}{
			\judgetype{\Gamma}{\eOOblame{l}}{T}
		}
	\end{gather*}

@@

\figref{fig:blame-static} defines the syntax of cast calculus and its
static semantics. It extends the syntax in \citet{siek2009exploring} with sum 
types and product types, and annotates function codomain explicitly. 
Its semantics depend on blame strategies, so we defer them to sub-sections.
\todo[inline]{Which previous definitions are you refering to?  What
  are the little changes? -Jeremy}
\todo[inline]{Fixed -KC}
\todo[inline]{The term typing rule for casts is broken. -Jeremy}

@@

Let $ e $ ranges over terms, including all terms from $ \mathtt{STLC+} $ and, 
in addition, casts and blame. Unlike $ \mathtt{STLC+} $, we annotate the 
codomain of lambda abstractions explicitly.
\todo[inline]{Why do you annotate the codomain of lambda abstractions
  explicitly? -Jeremy}
The end of \figref{fig:blame-static} shows the typing rules for the
additional terms.

Let $ o $ ranges over observations. They are what would be observed if a 
program terminates. Observations include all value constructors and blames.
\todo[inline]{``blames'' is incorrect. See
https://www.wordhippo.com/what-is/the-plural-of/blame.html}

@@

Let $ c $ ranges over casts. A cast is a triple of a type, a label, and a type.
\todo[inline]{``ranges'' should be ``range'', not plural. -Jeremy}
Let $ v $ ranges over values. A value is either a function, the 
element of unit, a pair, a left injection, a right injection, or a casted value.
The cast around a casted value is not arbitrary, as shown by value typing: the 
source type must be a pre-type, and the source and the target must be 
shallow-consistent.
Let $ r $ ranges over cast results. A cast result is either a success, which 
brings a value, or a failure, which brings a blame label.
Let $ s $ ranges over machine states. A state is either looking at an 
expression to decide what to do next, returning a value to a continuation, or 
halting with an observation.
Let $ \kappa $ ranges over continuations. $ \mathtt{mt} $ is the top 
continuation. The remaining continuations correspond to expressions. For 
example, $ (\mathtt{cons_1} \; e \; \rho \; \kappa) $ is the continuation where 
we are waiting for the value of the first argument to a $ \mathtt{cons} $. And 
the last continuation, $ \langle c \rangle \kappa $ is to cast the value before 
returning to $ \kappa $.

>>>>

\newcommand{\todoKCFixed}[0]{\todo[inline]{Fixed. -KC}}

@@

	Term typing
	\fbox{$ \judgetype{\Gamma}{e}{T} $}
	\begin{gather*}
		\inference{
			\Gamma \vdash e : T_1 & T_1 \sim T_2
		}{
			\judgetype{\Gamma}{\eOOcast{e}{T_1}{l}{T_2}}{T_2}
		} \quad
		\inference{
		}{
			\judgetype{\Gamma}{\eOOblame{l}}{T}
		}
	\end{gather*}

@@

\figref{fig:blame-static} defines the syntax of cast calculus and its
static semantics. It extends the syntax in \citet{siek2009exploring} with sum 
types and product types, and annotates function codomain explicitly. 
Its semantics depend on blame strategies, so we defer them to sub-sections.
\todo[inline]{Which previous definitions are you refering to?  What
  are the little changes? -Jeremy}
\todoKCFixed{}
\todo[inline]{The term typing rule for casts is broken. -Jeremy}
\todoKCFixed{}

@@

Let $ e $ ranges over terms, including all terms from $ \mathtt{STLC+} $ and, 
in addition, casts and blame. Unlike $ \mathtt{STLC+} $, we annotate the 
codomain of lambda abstractions explicitly.
\todo[inline]{Why do you annotate the codomain of lambda abstractions
  explicitly? -Jeremy}
\todo[inline]{Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC}
The end of \figref{fig:blame-static} shows the typing rules for the
additional terms.

Let $ o $ ranges over observations. They are what would be observed if a 
program terminates. Observations include all value constructors and blame.

@@

Let $ c $ range over casts. A cast is a triple of a type, a label, and a type.
Let $ v $ range over values. A value is either a function, the 
element of unit, a pair, a left injection, a right injection, or a casted value.
The cast around a casted value is not arbitrary, as shown by value typing: the 
source type must be a pre-type, and the source and the target must be 
shallow-consistent.
Let $ r $ ranges over cast results. A cast result is either a success, which 
brings a value, or a failure, which brings a blame label.
Let $ s $ ranges over machine states. A state is either looking at an 
expression to decide what to do next, returning a value to a continuation, or 
halting with an observation.
Let $ \kappa $ ranges over continuations. $ \mathtt{mt} $ is the top 
continuation. The remaining continuations correspond to expressions. For 
example, $ (\mathtt{cons_1} \; e \; \rho \; \kappa) $ is the continuation where 
we are waiting for the value of the first argument to a $ \mathtt{cons} $. And 
the last continuation, $ \langle c \rangle \kappa $ is to cast the value before 
returning to $ \kappa $.
